%-------------------------
% Anuj Gambhir — Master CV (Combined, All Experience)
%-------------------------
\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.35in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2 \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
\begin{document}

%---------- HEADER ----------
\begin{center}
    {\LARGE \scshape \textbf{Anuj Gambhir}} \\ \vspace{3pt}
    \small
    \href{tel:9599575254}{+91-9599575254} $|$
    \href{mailto:anujgambhir07@gmail.com}{anujgambhir07@gmail.com} $|$
    Delhi, India $|$
    \href{https://www.linkedin.com/in/anuj-gambhir-4651ab402/}{linkedin.com/in/anuj-gambhir-4651ab402} $|$
    \href{https://www.github.com/anujgambhir07}{github.com/anujgambhir07}
\end{center}
\vspace{-12pt}

%---------- SUMMARY ----------
\section{Summary}
\small{DTU B.Tech Biotechnology Engineering student (Class of 2028) with a multidisciplinary track record spanning \textbf{machine learning \& generative AI}, \textbf{IoT/embedded systems}, \textbf{full-stack \& UI/UX development}, \textbf{business strategy consulting}, \textbf{digital marketing \& sales}, and \textbf{biotechnology research}. Builds end-to-end ML/RAG pipelines and neural network models, ships LLM-powered product features, engineers IoT automation systems, and has driven measurable revenue outcomes in sales and marketing roles. Selected for the McKinsey Forward Programme; winner/finalist across multiple case and design competitions; 150+ DSA problems solved.}
\vspace{-4pt}

%---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Delhi Technological University (DTU)}{Delhi, India}
    {B.Tech in Biotechnology Engineering}{Aug 2024 -- May 2028}
    \resumeItemListStart
      \resumeItem{CGPA: \textbf{7.1/10} (after 3 semesters) $|$ JEE Mains 2024: \textbf{95.8 Percentile} $|$ JEE Advanced 2024: \textbf{Qualified} (Top $\sim$2.5\% nationally)}
      \resumeItem{Relevant Coursework: Linear Algebra, Probability \& Statistics, Data Structures \& Algorithms, Applied Mathematics}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-6pt}

%---------- SKILLS ----------
\section{Skills}
\begin{itemize}[leftmargin=0.12in, label={}, itemsep=1pt, parsep=0pt]
  \small{
    \item \textbf{ML \& AI:} Supervised/Unsupervised Learning, Deep Learning (CNNs, RNNs, Transformers), NLP, Generative AI, RAG, Reinforcement Learning Fundamentals, Agentic AI (learning), Hyperparameter Tuning, Model Evaluation
    \item \textbf{Frameworks \& Libraries:} PyTorch, TensorFlow/Keras, Scikit-learn, LangChain, LangGraph, HuggingFace Transformers, XGBoost, LightGBM, Pandas, NumPy, Matplotlib, Seaborn
    \item \textbf{Generative AI \& LLMs:} OpenAI, Claude, Gemini Pro APIs, Prompt Engineering, Multi-model Workflow Integration, DALL$\cdot$E, Midjourney, RunwayML
    \item \textbf{Data \& Engineering:} Python (Advanced), SQL (window functions, CTEs, query optimization), C++, ETL Pipelines, Feature Engineering, Statistical Analysis, REST APIs
    \item \textbf{BI \& Visualization:} Power BI, Tableau, MS Excel (Advanced)
    \item \textbf{IoT \& Hardware:} Arduino, ESP32/ESP8266, Sensor Integration (pH, EC, turbidity, LDR, temperature-humidity), Relay Automation, Embedded Systems, ADC Data Acquisition
    \item \textbf{Business \& Strategy:} Go-to-Market Strategy, Market Research, Competitive Analysis, MECE Frameworks, Financial Modeling, Business Case Development, Stakeholder Communication
    \item \textbf{Sales \& Marketing:} Client Acquisition, Negotiation, Lead Generation, Google Ads, Meta Ads Manager, Social Media Marketing, Campaign Strategy \& Optimization, CRM Basics
    \item \textbf{Design \& Creative:} Figma, Adobe Illustrator, Adobe Premiere Pro, After Effects, Canva, WordPress, Framer
    \item \textbf{Tools:} Git/GitHub, Docker, Jupyter, Google Colab, VS Code, LaTeX
    \item \textbf{Languages:} English (Fluent), German (A1, in progress)
  }
\end{itemize}
\vspace{-6pt}

%---------- EXPERIENCE ----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {5G Research Intern}{DTU Campus}
    {DTU 5G Lab Summer Internship Programme, Dept. of ECE}{Jun 2026 -- Present}
    \resumeItemListStart
      \resumeItem{Built Python data pipelines (NumPy/Pandas) processing 5G network telemetry streams; conducted statistical analysis across \textbf{10+ performance variables} to model throughput behavior under variable load conditions.}
      \resumeItem{Prototyped \textbf{ML-based anomaly detection} on radio access network (RAN) data, isolating latency outliers and packet degradation patterns across multi-node test environments, achieving \textbf{87\% precision} on held-out test sets.}
    \resumeItemListEnd

  \resumeSubheading
    {Website \& UI/UX Developer}{Remote}
    {Freelance / Agency Collaborations}{2025 -- Present}
    \resumeItemListStart
      \resumeItem{Developed responsive websites using WordPress, HTML, CSS, and JavaScript for freelance and agency clients.}
      \resumeItem{Specialized in modern UI/UX design workflows using Figma, Framer, and WordPress.}
    \resumeItemListEnd

  \resumeSubheading
    {IoT Data \& Automation Intern}{NSUT Campus}
    {HHTRF Lab, Netaji Subhas University of Technology}{Jul 2025 -- Dec 2025}
    \resumeItemListStart
      \resumeItem{Engineered an automated \textbf{ESP32 data acquisition pipeline} integrating pH, EC, temperature-humidity, LDR, and fluid control sensor modules for real-time environmental monitoring.}
      \resumeItem{Developed statistical sensor-fusion frameworks and calibration logic to optimize ingestion accuracy and real-time tracking reliability; implemented relay-based actuation for smart irrigation and fluid management workflows.}
    \resumeItemListEnd

  \resumeSubheading
    {McKinsey Forward Programme --- Participant}{Remote}
    {McKinsey \& Company}{12 Weeks, 2025}
    \resumeItemListStart
      \resumeItem{Selected into a globally limited cohort; mastered structured problem-solving, data-driven decision frameworks, and hypothesis-led analytical storytelling.}
      \resumeItem{Completed \textbf{8+ quantitative business case analyses} using MECE frameworks and financial modeling, delivering executive-level strategic recommendations across diverse industry verticals.}
    \resumeItemListEnd

  \resumeSubheading
    {Freelance Digital Marketing Specialist}{Remote}
    {Self-Employed}{Jun 2024 -- Present}
    \resumeItemListStart
      \resumeItem{Managed social media accounts for multiple brands across Instagram, Facebook, and LinkedIn; developed content calendars and copy, scheduling via Meta Business Suite and Buffer.}
      \resumeItem{Operated and optimized \textbf{Google Ads} (Search, Display, Shopping) and \textbf{Meta Ads} campaigns for e-commerce clients; analyzed platform insights to increase reach, engagement, and conversions.}
    \resumeItemListEnd

  \resumeSubheading
    {Online Educator (IB, IGCSE, JEE)}{Remote}
    {Freelance}{2024 -- Present}
    \resumeItemListStart
      \resumeItem{Taught Physics, Chemistry, and Mathematics to IB, IGCSE, and JEE students through personalized online sessions and custom curriculum design.}
    \resumeItemListEnd

  \resumeSubheading
    {Video Editor \& Creative Designer}{DTU Campus}
    {R3PRSNT (DTU Hip-Hop Society) $|$ Rotaract Club $|$ BioSoc DTU $|$ Freelance}{2024 -- Present}
    \resumeItemListStart
      \resumeItem{Produced and edited \textbf{20+ promotional videos}, reels, and event creatives across 3 student organizations and freelance clients using Adobe Premiere Pro, After Effects, and Illustrator.}
      \resumeItem{Designed brand identity materials and social media visuals; managed end-to-end visual content pipeline for academic and NGO events, ensuring consistent brand communication.}
    \resumeItemListEnd

  \resumeSubheading
    {AI-Augmented Full-Stack Developer \& UI/UX Intern}{Remote}
    {TrueCompanion}{Jun 2024 -- Sep 2024}
    \resumeItemListStart
      \resumeItem{Integrated Claude, Gemini Pro, and OpenAI APIs into live product architecture via multi-model workflows, cutting feature deployment cycles by \textbf{40\%}.}
      \resumeItem{Audited \textbf{10,000+ user interaction records} to surface UX bottlenecks; resolved 10+ UI inconsistencies and refactored front-end based on behavioral data, lifting cross-device performance scores by \textbf{25\%}.}
      \resumeItem{Optimized WordPress pages for layout and performance, reducing reported UI-related support issues, and collaborated with the product team on service-based feature improvements.}
    \resumeItemListEnd

  \resumeSubheading
    {Sales Manager \& Campaign Strategist}{Delhi-NCR}
    {Delhi-based Educational Organization}{Jun 2024 -- Aug 2024}
    \resumeItemListStart
      \resumeItem{Initiated and closed tie-ups with \textbf{130+ institutes} across Delhi-NCR; built a verified institute database independently.}
      \resumeItem{Generated a potential sales pipeline worth \textbf{Rs. 75 lakh} at age 18, significantly contributing to company targets through data collection, relationship building, and first-contact conversion strategies.}
    \resumeItemListEnd

  \resumeSubheading
    {Biotechnology Research Intern}{DTU Campus}
    {Department of Biotechnology, Delhi Technological University}{2024}
    \resumeItemListStart
      \resumeItem{Conducted independent research on the biosynthesis of iron oxide nanoparticles using \textit{Bacillus} bacteria, combining microbiology with nanobiotechnology applications.}
      \resumeItem{Executed wet-lab experimentation, culture optimization, and nanoparticle synthesis workflows; operated material characterization instruments under departmental research supervision.}
    \resumeItemListEnd

  \resumeSubheading
    {Private Tutor (PCM Subjects)}{Remote}
    {Self-Employed}{Feb 2022 -- Present}
    \resumeItemListStart
      \resumeItem{Tutored high school students in Physics, Chemistry, and Mathematics; developed personalized study plans and doubt-solving sessions, improving academic performance and engagement.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6pt}

%---------- PROJECTS ----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{LangChain-Powered RAG Knowledge Assistant} $|$ \textit{Python, LangChain, LangGraph, FAISS, OpenAI API}}{2026}
    \resumeItemListStart
      \resumeItem{Architected a Retrieval-Augmented Generation pipeline using LangChain and LangGraph to build a domain-specific Q\&A assistant over large unstructured document corpora.}
      \resumeItem{Implemented a FAISS vector store for semantic similarity search across embedded document chunks; integrated multi-hop reasoning via LangGraph agent workflows for complex, multi-step queries.}
      \resumeItem{Benchmarked retrieval accuracy, latency, and hallucination rate against baseline GPT-4 prompting; reduced hallucination incidence by \textbf{62\%} on a domain-specific evaluation set.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Sentiment Analysis \& Review Classification Engine} $|$ \textit{Python, PyTorch, HuggingFace, BERT, Flask, Docker}}{2026}
    \resumeItemListStart
      \resumeItem{Fine-tuned a pre-trained BERT transformer on 50K+ e-commerce reviews for multi-class sentiment classification, achieving \textbf{91.4\% validation accuracy}.}
      \resumeItem{Implemented the full ML pipeline: preprocessing, HuggingFace tokenization, attention-based fine-tuning, and evaluation using precision/recall/F1 with cross-validation.}
      \resumeItem{Deployed as a Flask REST API with batch inference support, containerized using Docker for reproducible, real-time product-feedback scoring.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Customer Churn Prediction via Ensemble ML} $|$ \textit{Scikit-learn, XGBoost, LightGBM, SQL, Power BI}}{2025}
    \resumeItemListStart
      \resumeItem{Built an end-to-end churn prediction model on a 100K-row telecom dataset; engineered 25+ features via domain-driven selection, handling class imbalance with SMOTE oversampling.}
      \resumeItem{Benchmarked Logistic Regression, Random Forest, XGBoost, and LightGBM via grid search and cross-validation, achieving \textbf{AUC-ROC of 0.94}.}
      \resumeItem{Connected model outputs to a live Power BI dashboard via SQL pipelines, delivering churn-risk segmentation and interpretability reports.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Multi-Platform Creator Analytics Platform} $|$ \textit{Python, Meta/YouTube APIs, ETL, Pandas}}{2025 -- Present}
    \resumeItemListStart
      \resumeItem{Engineered a full-stack analytics platform aggregating \textbf{500K+ daily data points} across Instagram and YouTube via Meta/YouTube Data API integrations.}
      \resumeItem{Built Python ETL scripts to normalize multi-platform JSON payloads into a unified schema; developed statistical trend models to predict content performance and surface growth-driving insights.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{AI-Assisted Application Prototypes} $|$ \textit{Python, Generative AI, LLM APIs, Agentic AI}}{2024 -- Present}
    \resumeItemListStart
      \resumeItem{Developed multiple experimental apps leveraging generative AI APIs and prompt engineering for task automation.}
      \resumeItem{Explored agentic AI workflows to prototype intelligent, multi-step automation pipelines as part of self-directed ML learning.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Smart Water Quality Monitoring System} $|$ \textit{Arduino, IoT, Python, Sensor Fusion}}{2024}
    \resumeItemListStart
      \resumeItem{Built a real-time IoT system integrating 4 sensors (pH, turbidity, temperature, moisture) with live output to a mobile app and LCD display.}
      \resumeItem{Wrote firmware and data-pipeline logic in Python/C; designed the full hardware circuit and relay automation architecture, applying signal processing for stable readings.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Hydroponic Automation System} $|$ \textit{ESP32, IoT, Relay Automation}}{2024}
    \resumeItemListStart
      \resumeItem{Engineered an automated irrigation prototype using ESP32 microcontrollers and soil moisture sensors, implementing relay-based actuation logic that eliminated manual water cycles.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Iron Oxide Nanoparticle Biosynthesis} $|$ \textit{Biotechnology, Microbiology, Wet Lab}}{2024}
    \resumeItemListStart
      \resumeItem{Independently synthesized iron oxide nanoparticles via \textit{Bacillus} bacteria; operated characterization instruments in a university research lab.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6pt}

%---------- ACHIEVEMENTS ----------
\section{Achievements \& Certifications}
\begin{itemize}[leftmargin=0.12in, label={}, itemsep=2pt, parsep=0pt]
  \small{
    \item \textbf{Case \& Business Competitions:} \textbf{1st} --- SCEE DTU Case Competition (Go-to-Market \& Marketing Expansion Frameworks) $|$ \textbf{3rd} --- DTU East Campus Case Competition (Corporate Strategy \& Operational Turnaround) $|$ \textbf{Top 5} --- Marksoc DTU Marketing Challenge $|$ \textbf{Winner} --- Brand Blend Challenge
    \item \textbf{Design Competitions:} \textbf{Winner} --- Presentation Design Competition $|$ Multiple college-level design awards
    \item \textbf{Sales \& Business:} Built a verified database of \textbf{130+ institutes} independently; drove a potential business pipeline of \textbf{Rs. 75 lakh} at age 18 as Sales Manager
    \item \textbf{Coursework \& Practice:} ML/DL: Supervised Learning, CNNs, RNNs, Transformers, Dimensionality Reduction, GenAI/LLMs $|$ Advanced SQL: window functions, CTEs, query optimization $|$ 150+ DSA problems on LeetCode/Codeforces (Python/C++) $|$ German: A1 in progress
  }
\end{itemize}

\end{document}
